Summer 2024 Report

### 2024-12-16 Relations/Report.tex
ARS

\begin{document}
\renewcommand{\arraystretch}{1.3}

@@

@@

\subsection*{November 21}
Four local ``normal form properties'':
\begin{enumerate}
  \item $WNFP(a) : \forall n \in NF. (a \tto n) \to \forall b. (a \tto b) \to (b \tto n)$
    "$a$ all reducts of $a$ reduce to $a$'s normal form, if it exists``
  \item $NFP(a) : \forall n \in NF. (a \tto n) \to \forall b. (a \thlra b) \to (b \tto n)$
    "$a$ all converta of $a$ reduce to $a$'s normal form, if it exists``
  \item $WUN(a) : \forall n m \in NF. (a \tto n) \to (a \tto m) \to n \equiv m$
    "$a$ is reducible to at most one normal form"
  \item $UN(a) : \forall n m \in NF. (a \thlra n) \to (a \thlra m) \to n \equiv m$
    "$a$ is convertible to at most one normal form''
\end{enumerate}

\subsection{Notes from 08.29}
\begin{enumerate}
  \item Finish formulating the ``compactness property".  Two candidates:
  \begin{itemize}
    \item ``Every cocone for a given infinite sequence loops back to some point in the sequence"
    \item ``If an $R^*$-sequence has a cocone then it's constant after some point on.''
  \end{itemize}
\end{enumerate} \sacomment{This is our recurrence property right? If so, we can just delete this.}

@@

>>>>

\newcommand{\down}[1]{{#1}{\downarrow}}
\begin{document}
\renewcommand{\arraystretch}{1.3}

@@

\apcomment{For a property $P(x)$, let $\down{P}(x) := \forall y. x \thra y \implies P(y)$}

Note that $\down{P} \subseteq P$.

If the converse inclusion holds, we will say that $P$ is \emph{closed under reduction}.

@@

\subsection*{November 21}
\apcomment{These may be addressed by the implications table}
Four local ``normal form properties'':
\begin{enumerate}
  \item $WNFP(a) : \forall n \in NF. (a \tto n) \to \forall b. (a \tto b) \to (b \tto n)$
    "$a$ all reducts of $a$ reduce to $a$'s normal form, if it exists``
  \item $NFP(a) : \forall n \in NF. (a \tto n) \to \forall b. (a \thlra b) \to (b \tto n)$
    "$a$ all converta of $a$ reduce to $a$'s normal form, if it exists``
  \item $WUN(a) : \forall n m \in NF. (a \tto n) \to (a \tto m) \to n \equiv m$
    "$a$ is reducible to at most one normal form"
  \item $UN(a) : \forall n m \in NF. (a \thlra n) \to (a \thlra m) \to n \equiv m$
    "$a$ is convertible to at most one normal form''
\end{enumerate}

@@

  \apcomment{This implication should be either proved or refuted.}
